Supermassive black hole and host spheroid affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram

### 2015-07-17 papers/MbhMsph/ApJ_submission/mm.tex
submission day

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
We present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight %\emph{early-type sequence} 
\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$.
At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
\emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
(most elliptical galaxies contain disks, i.e.~$L_{\rm sph} \neq L_{\rm gal}$) --
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

\keywords{galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure; black hole physics}

@@

assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$.} 

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
Four spiral galaxies had their magnitudes overestimated (luminosities underestimated) and are shown as upper limits. 
The red dashed line indicates the BCES bisector linear regression for the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
$M_{\rm BH}$ correlates equally well with $L_{\rm gal}$ and $L_{\rm sph}$ only for early-type galaxies, 
but not for all (early+late-type) galaxies. }
\label{fig:mbhmaggal}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols have the same meaning as in Figure \ref{fig:mbhmaggal}.
The red dashed line indicates the BCES bisector linear regression for the spheroidal component of the 45 early-type (E+S0) galaxies, 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for the core-S\'ersic and S\'ersic spheroids, respectively.}
\label{fig:mbhmagsph}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_sph_psb.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude (as in Figure \ref{fig:mbhmagsph}). 
Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
Bulges with $n_{\rm sph}<2$, claimed by some to be pseudo-bulges, are enclosed with a square. 
The black solid line shows the BCES bisector linear regression for the spheroids that have $n_{\rm sph} \geq 2$, 
such that $M_{\rm BH} \propto L_{\rm sph}^{1.25 \pm 0.13}$. }
\label{fig:pseudob}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/inset_psb.pdf}
\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$ (see Figure \ref{fig:pseudob}), 
plotted against $n_{\rm sph}$. 
The vertical dashed line corresponds to $n_{\rm sph} = 2$.
The horizontal solid line is equivalent to a zero vertical offset.
Among the bulges with $n_{\rm sph}<2$, 12 have a positive vertical offset and 11 have a negative vertical offset.
Hence, bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
\label{fig:offset}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
\caption{Black hole mass plotted against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type (see legend).
The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
a near-linear relation consistent with a dry-merging formation scenario.
The steeper blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge grows in stellar mass. 
We note that AGNs with $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a} appear to follow the blue line 
(see Graham et al. 2015, \emph{in preparation}).}
\label{fig:mbhmasssph}
\end{center}
\end{figure}

@@

\begin{itemize}
\item The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the spheroidal components of early-type (elliptical + lenticular) galaxies 
      has a slope of $1.04 \pm 0.10$ and intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
      We call this tight correlation an \emph{early-type sequence}. 
      The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the bulges of late-type (spiral) galaxies has a slope of $2-3$,
      which is less well constrained due to
      the smaller size of the subsample and, more importantly, the smaller range in spheroid stellar mass 
      ($3 \times 10^9 \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 3 \times 10^{10}$) that the subsample spans. 
      We refer to this correlation as a ``tentative'' \emph{late-type sequence}. 
      In (gas-poor) early-type galaxies, the black hole and the stellar content of the spheroidal component grow at the same pace, 
      following a linear $M_{\rm BH} - M_{\rm *,sph}$ relation. 
      In (gas-rich) spiral galaxies, the black hole grows faster than its host bulge, 
      following a quadratic/cubic $M_{\rm BH} - M_{\rm *,sph}$ relation. 
      Unsurprisingly, in a color-magnitude diagram\footnote{Total $B-V$ colors, 
      corrected for inclination, Galactic extinction and K-correction, 
      were taken from the HyperLEDA online database \citep{hyperleda}.}, 
      our early- and late-type galaxies occupy the two distinct regions of the red sequence and the blue cloud, respectively. 
      For analogy with this, we refer to our \emph{early-type sequence} as a \emph{red sequence} 
      and to our \emph{late-type sequence} as a \emph{blue sequence}. 
      %For analogy with the color-magnitude diagram, 
      %it may be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence} 
      %and to our \emph{late-type sequence} as a \emph{blue sequence}.
      %Future work will explore the color of spheroids and galaxies in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.  
\item The $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$. 
      This value is dramatically larger than what previously reported ($0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}).
\item The $M_{\rm BH} - M_{\rm *,sph}$ log-relations for core-S\'ersic and S\'ersic spheroids have slopes consistent with each other 
      ($1.19 \pm 0.23$ and $1.48 \pm 0.20$, respectively), 
      thus these two populations do not appear to define two distinct sequences. 
\item In the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagram, for early-type galaxies, 
      we did not observe the change in slope required for consistency with the log-linear $M_{\rm BH} - \sigma$ and bent $L_{\rm sph} - \sigma$ correlations.
      This issue of inconsistency remains therefore an open question. 
      It might be that we are still not probing enough low-mass black holes ($M_{\rm BH} < 10^7\rm~M_\odot$) 
      for the subsample of early-type galaxies, 
      or that the transition from  $L_{\rm sph} \propto \sigma^2$ at low luminosities to $L_{\rm sph} \propto \sigma^{(5-6)}$ at high luminosities 
      is less sharp than previously thought.
      We intend to investigate this point in our future work. 
\item Spheroids with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. 
\item The $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations have the same level of intrinsic scatter 
      when considering early-type galaxies only. 
      Once reasonable numbers of spiral galaxies are included, 
      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$. 
\end{itemize}

@@

\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}

>>>>

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
We present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
and define a tight %\emph{early-type sequence} 
\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
\emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by the current bulge sample with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
(most elliptical galaxies contain disks, i.e.~$L_{\rm sph} \neq L_{\rm gal}$) --
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

\keywords{black hole physics; galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure}

@@

assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$. 
Absolute luminosities were not corrected for cosmological redshift dimming 
(this correction would be as small as $-0.02\rm~mag$ for galaxies at a distance of $40\rm~Mpc$ 
or $-0.05\rm~mag$ for galaxies at a distance of $100\rm~Mpc$).} 

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{mbh_vs_mag_tot.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
Four spiral galaxies had their magnitudes overestimated (luminosities underestimated) and are shown as upper limits. 
The red dashed line indicates the BCES bisector linear regression for the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
$M_{\rm BH}$ correlates equally well with $L_{\rm gal}$ and $L_{\rm sph}$ only for early-type galaxies, 
but not for all (early+late-type) galaxies. }
\label{fig:mbhmaggal}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{mbh_vs_mag_sph.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude. 
Symbols have the same meaning as in Figure \ref{fig:mbhmaggal}.
The red dashed line indicates the BCES bisector linear regression for the spheroidal component of the 45 early-type (E+S0) galaxies, 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The black dashed-dotted and dotted lines represent the BCES bisector linear regressions for the core-S\'ersic and S\'ersic spheroids, respectively.}
\label{fig:mbhmagsph}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{mbh_vs_mag_sph_psb.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ spheroid absolute magnitude (as in Figure \ref{fig:mbhmagsph}). 
Symbols are color coded according to the spheroid S\'ersic index $n_{\rm sph}$. 
Bulges with $n_{\rm sph}<2$, claimed by some to be pseudo-bulges, are enclosed with a square. 
The black solid line shows the BCES bisector linear regression for the spheroids that have $n_{\rm sph} \geq 2$, 
such that $M_{\rm BH} \propto L_{\rm sph}^{1.25 \pm 0.13}$. }
\label{fig:pseudob}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{inset_psb.pdf}
\caption{Vertical offset from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph} \geq 2$ (see Figure \ref{fig:pseudob}), 
plotted against $n_{\rm sph}$. 
The vertical dashed line corresponds to $n_{\rm sph} = 2$.
The horizontal solid line is equivalent to a zero vertical offset.
Among the bulges with $n_{\rm sph}<2$, 12 have a positive vertical offset and 11 have a negative vertical offset.
Hence, bulges with $n_{\rm sph}<2$ are not randomly offset to lower black hole masses 
from the correlation traced by bulges with $n_{\rm sph} \geq 2$.}
\label{fig:offset}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{mbh_vs_mass_sph.pdf}
\caption{Black hole mass plotted against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type (see legend).
The red dashed line indicates the BCES bisector linear regression for the bulges of the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
a near-linear relation consistent with a dry-merging formation scenario.
The steeper blue solid line shows the BCES bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The bulges of late-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently (``quadratically'' or ``cubically'') than the host bulge grows in stellar mass. 
We note that AGNs with $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a} appear to follow the blue line 
(see Graham et al. 2015, \emph{in preparation}).}
\label{fig:mbhmasssph}
\end{center}
\end{figure}

@@

\begin{itemize}
\item The logarithmic $M_{\rm BH} - M_{\rm *,sph}$ relation for the spheroidal components of early-type (elliptical + lenticular) galaxies 
      has a slope of $1.04 \pm 0.10$ and intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
      We call this tight correlation an \emph{early-type sequence}. 
      The $M_{\rm BH} - M_{\rm *,sph}$ log-relation for the bulges of late-type (spiral) galaxies has a slope of $2-3$,
      which is less well constrained due to
      the smaller size of the subsample and, more importantly, the smaller range in spheroid stellar mass 
      ($3 \times 10^9 \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 3 \times 10^{10}$) that the subsample spans. 
      We refer to this correlation as a \emph{late-type sequence}. 
      In (gas-poor) early-type galaxies, the black hole and the stellar content of the spheroidal component grow at the same pace, 
      following a linear $M_{\rm BH} - M_{\rm *,sph}$ relation. 
      In (gas-rich) spiral galaxies, the black hole grows faster than its host bulge, 
      following a quadratic/cubic $M_{\rm BH} - M_{\rm *,sph}$ relation. 
      Unsurprisingly, in a color-magnitude diagram\footnote{Total $B-V$ colors, 
      corrected for inclination, Galactic extinction and K-correction, 
      were taken from the HyperLEDA online database \citep{hyperleda}.}, 
      our early- and late-type galaxies occupy the two distinct regions of the red sequence and the blue cloud, respectively. 
      For analogy with this, we refer to our \emph{early-type sequence} as a \emph{red sequence} 
      and to our \emph{late-type sequence} as a \emph{blue sequence}. 
      %For analogy with the color-magnitude diagram, 
      %it may be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence} 
      %and to our \emph{late-type sequence} as a \emph{blue sequence}.
      %Future work will explore the color of spheroids and galaxies in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.  
\item The median $M_{\rm BH}/M_{\rm *,sph}$ ratio for the early-type galaxies is $0.68 \pm 0.04\%$. 
      This value is dramatically larger than what was previously reported ($0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}), 
      but in close agreement with the value of $0.49\%$ reported by \cite{grahamscott2013} for core-S\'ersic spheroids. 
\item The logarithmic $M_{\rm BH} - M_{\rm *,sph}$ relations for the core-S\'ersic and S\'ersic spheroids 
      have slopes with over-lapping uncertainties ($1.19 \pm 0.23$ and $1.48 \pm 0.20$, respectively).  
      The S\'ersic relation is less steep than, but also has over-lapping uncertainties with, 
      the slope of $2.22 \pm 0.58$ reported by \cite{scott2013} for S\'ersic spheroids.  
      The distinction between core-S\'ersic and S\'ersic spheroids found by \cite{scott2013} is thus less pronounced here. 
\item In the $M_{\rm BH} - L_{\rm sph}$ (or $M_{\rm BH} - M_{\rm *,sph}$) diagram, for early-type galaxies, 
      we did not observe the change in slope required for consistency with the log-linear $M_{\rm BH} - \sigma$ and bent $L_{\rm sph} - \sigma$ correlations.
      This issue of inconsistency remains therefore an open question. 
      It might be that we are still not probing enough low-mass black holes ($M_{\rm BH} < 10^7\rm~M_\odot$) 
      for the subsample of early-type galaxies, 
      or that the transition from  $L_{\rm sph} \propto \sigma^2$ at low luminosities to $L_{\rm sph} \propto \sigma^{(5-6)}$ at high luminosities 
      is less sharp than previously thought.
      We intend to investigate this point in our future work. 
\item Spheroids with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. 
\item The $M_{\rm BH} - L_{\rm gal}$ and $M_{\rm BH} - L_{\rm sph}$ correlations have the same level of intrinsic scatter 
      when considering early-type galaxies only. 
      Once reasonable numbers of spiral galaxies are included, 
      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$. 
\end{itemize}

Finally, we note that some of the literature-sourced black hole mass measurements used by \cite{kormendyho2013} are different from those used here.  
While these differences are smaller than $18\%$ for $78\%$ of the galaxies, 
in three cases (NGC 0821, NGC 4291, and NGC 3393) they are larger than a factor of $2.3$.  
We repeated our entire analysis using only the 58 galaxies that are in common between our sample and the sample of \cite{kormendyho2013}, 
assuming for these galaxies the black hole mass measurements published by \cite{kormendyho2013}. 
In doing so, we found that none of our conclusions changed.

@@

\bibliography{SMBHbibliography}
